Latitudinal gradients in biotic niche breadth vary across ecosystem types.

### 2018-01-30 manuscript/latitudepaper.tex
added updated results

  Link density (mean number of feeding links per species), generality (mean
  number of prey per species), and vulnerability (mean number of predators per
  species) were strongly and positively correlated ($R^2$=0.891 for link
  density and generality, $R^2$\textgreater0.999 for link density and
  vulnerability, and $R^2$=0.890 for generality and vulnerability). Contrary
  to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) did not include a significant
  effect of latitude on species richness for any ecosystem type. Further, there were no significant
  relationships between link density, generality, or vulnerability with
  latitude for any ecosystem type.

  Each measure of specialisation increased with increasing
  species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
  $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term 
  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).

>>>>

  Link density (mean number of feeding links per species), generality (mean
  number of prey per species), and vulnerability (mean number of predators per
  species) were strongly and positively correlated ($R^2$=0.891 for link
  density and generality, $R^2$\textgreater0.999 for link density and
  vulnerability, and $R^2$=0.890 for generality and vulnerability). Contrary
  to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) did not include a significant
  effect of latitude on species richness for any ecosystem type. Further, there were no significant
  relationships between link density, generality, or vulnerability with
  latitude for any ecosystem type.
  [[After correction: $R^2$=0.865 for link density and generality, $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.865 for generality and vulnerability.]]

  Each measure of specialisation increased with increasing
  species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
  $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
  Fig.~\ref{props_v_lat}). 
  [[After correction: ($\beta_0$=0.689, $p$\textless0.001; $\beta_0$=0.687, $p$\textless0.001; and $\beta_0$=0.690, $p$\textless0.001, respectively).]]
  For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). 
  [[After correction: $\beta_{Latitude}$=-0.0004, $p$=0.890 for link density; $\beta_{Latitude}$=-0.001, $p$=0.640 for generality; and $\beta_{Latitude}$=-0.0004, $p$=0.889 for vulnerability.]]
  In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term 
  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
  [[After correction: Link density scaled less strongly with species richness in stream and terrestrial food webs ($\beta_{Stream}$=-0.099, $p$\textless0.001; $\beta_{Terrestrial}$=-0.116, $p$\textless0.001) but there was no scaling of link density with latitude for any property. Scaling of generality with latitude, however, was significantly stronger in lake food webs than other ecosystem types and slightly, but not significantly, stronger in stream food webs ($\beta_{Latitude:Lake}$=0.005, $p$=0.001; $\beta_{Latitude:Stream}$=0.003, $p$=0.117). Vulnerability, like link density, did not scale with latitude for any property and scaled more weakly with species richness in stream and terrestrial food webs ($\beta_{Stream}$=-0.099, $p$\textless0.001; $\beta_{Terrestrial}$=-0.116, $p$\textless0.001).]]

  [[Note: The trophic species version of the webs changed less with the correction. For link density, $\beta_{Latitude:Lake}$=0.005, $p$=0.002. For generality, $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001 and $\beta_{Latitude:Stream}$=0.004, $p$=0.009. For vulnerability, $\beta_{Latitude:Lake}$=0.005, $p$=0.002.]]
